---
title: "Food processing breakout validation figures"
output: 
  html_document: 
    toc: yes
    code_folding: hide
    fig_width: 8
    fig_height: 6
editor_options:
  chunk_output_type: console
---

```{r setup, include=FALSE, warning = FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(knitr)
```

```{r, message = FALSE, warning = FALSE}
# load necessary packages and data
library(tidyr)
library(dplyr)
library(readr)
library(plotly)
library(ggplot2)
library(jgcricolors)
library(ggsci)
library(Polychrome)

# set directories
run_dir <- "C:/Users/spei632/Documents/GCAM_industry/food_processing/initial_breakout_results/data/food_processing_run_8-7-23"
fig_dir <- paste0(run_dir,"/figures_validation")
if (!dir.exists(fig_dir)) {dir.create(fig_dir)}
results_dir <- fig_dir
setwd(run_dir)

# load functions
source("C:/Users/spei632/Documents/GCAM_industry/food_processing/initial_breakout_results/parse_PIC_data.R")

# load data
queries <- list.files(run_dir, pattern = 'queryoutall')
for (i in queries) {
  filename <- gsub('.csv','', i) %>% gsub('queryoutall_','', .)
  if (!grepl("food_pro", filename)) {
    assign(filename, read_csv(paste0(run_dir, "/", i), skip = 1) %>% 
             parse_PIC_data() %>%
             # indicate if master or food processing branch
             mutate(branch = if_else(grepl("date=2023-7-8", date), "food_industry", "master")))
  } else {
    # if it is a food processing query, there will be no results for some of the scenarios, and we need to handle separately
    # figure out which line to skip to
    temp <- read_csv(paste0(run_dir, "/", i), col_names = FALSE)
    index_start <- which(grepl("scenario", temp$X1))
    assign(filename, read_csv(paste0(run_dir, "/", i), skip = index_start - 1, comment = "food processing CO2 emissions by tech (excluding resource production) had error:") %>% 
             parse_PIC_data() %>%
             # indicate if master or food processing branch
             mutate(branch = if_else(grepl("date=2023-7-8", date), "food_industry", "master")))
    rm(temp)
    rm(index_start)
  }
}

# load GTAP data
CostShare_FoodProcessing_GTAP <- read_csv("C:/Users/spei632/Documents/GCAM_industry/food_processing/initial_exploration/data/CostShare_FoodProcessing_GTAP.csv")

# mappings
GWP_AR5 <- read_csv("C:/Users/spei632/Documents/GCAM_industry/food_processing/mappings/GWP_AR5.csv")
industry_sector_agg <- read_csv("C:/Users/spei632/Documents/GCAM_industry/food_processing/mappings/industry_sector_agg.csv")

# constants
C_to_CO2 <- 44/12

# get color palettes
pal_sel <- jgcricol()$pal_all
pal_sel_extended <- c(pal_sel, "food processing" = "mediumpurple", "biomass cogen" = "seagreen3",
                      "coal cogen" = "dimgray", "gas cogen" = "skyblue2", "gas with solar" = "lightblue",
                      "refined liquids cogen" = "lightpink", "district heat" = "darkslategray",
                      "process heat food processing" = "mediumpurple1", "electricity with solar" = "antiquewhite2", "electric heat pump" = "lavenderblush3")
data(palette36)
palette36 <- unname(palette36)
pal_industry_sectors <- c("agricultural energy use" = "burlywood3", "aluminum" = "lightsalmon", "cement" = "khaki2", "chemical" = "lightblue",               "construction" = "plum", "food processing" = "red", "iron and steel" = "palegreen3", "mining energy use" = "tan3", "N fertilizer" = "pink", "other industry" = "lightgray", "paper" = "wheat")

# scenarios to select
ref_scenario_name <- "Reference"
ref_scenario_name_master <- "GCAM"
food_branch_name <- "food_industry"
master_branch_name <- "master"

# industry sectors
industry_sectors <- unique(industry_shrwts_subsector$sector)
```

# Food processing sector breakout branch results

## Reference scenario

### Food processing sector outputs

Food processing output - just confirming that this matches food demand.

```{r, message = FALSE, warning = FALSE}
# aggregate food demand to total calories
food_demand_total <- food_demand %>%
  group_by(scenario, branch, Units, region, year) %>%
  summarize(value = sum(value)) %>%
  ungroup()

food_demand_total_food_pro_total_output <- food_demand_total %>%
  mutate(sector = "food demand") %>%
  bind_rows(food_pro_prod_region %>% dplyr::select(Units, scenario, branch, region, year, sector, value))

ggplot(food_demand_total_food_pro_total_output %>% 
         filter(scenario == ref_scenario_name & branch == food_branch_name & year >= 2005),
       aes(x = year, y = value, color = region)) +
  geom_line() +
  facet_wrap(~sector, ncol = 2, scale = "free_y") +
  scale_color_manual(values = palette36) +
  labs(x = "", y = "Pcal", title = "Food processing and food demand output by region, reference scenario, food industry branch") +
  theme_bw() +
  theme(text=element_text(size=22),
        strip.background = element_blank(),
        legend.position = "bottom")
ggsave(paste0(fig_dir, "/food_pro_food_demand_ref_food_ind.png"), width = 20, height = 15)
```

Process heat food processing output by technology.

```{r, message = FALSE, warning = FALSE}
food_pro_process_heat_prod_tech_heat_only <- food_pro_process_heat_prod_tech %>%
  filter(output == "process heat food processing")

ggplot(food_pro_process_heat_prod_tech_heat_only %>% 
         filter(scenario == ref_scenario_name & branch == food_branch_name & year >= 2005),
       aes(x = year, y = value, fill = technology)) +
  geom_col() +
  facet_wrap(~region, ncol = 8, scale = "free_y") +
  scale_fill_manual(values = pal_sel_extended, drop = TRUE, limits = force, name = "technology") +
  labs(x = "", y = "EJ", title = "Outputs of process heat food processing by technology, reference scenario, food industry branch") +
  theme_bw() +
  theme(text=element_text(size=22),
        strip.background = element_blank())
ggsave(paste0(fig_dir, "/food_pro_process_heat_outputs_by_tech_ref_food_ind.png"), width = 30, height = 20)

ggplot(food_pro_process_heat_prod_tech_heat_only %>% 
         filter(scenario == ref_scenario_name & branch == food_branch_name & year >= 2005),
       aes(x = year, y = value, fill = technology)) +
  geom_col() +
  scale_fill_manual(values = pal_sel_extended, drop = TRUE, limits = force, name = "technology") +
  labs(x = "", y = "EJ", title = "Global outputs of process heat food processing by technology\nReference scenario, food industry branch") +
  theme_bw() +
  theme(text=element_text(size=17),
        strip.background = element_blank())
ggsave(paste0(fig_dir, "/food_pro_process_heat_outputs_by_tech_ref_food_ind_global.png"), width = 10, height = 8)
```

### Food processing sector energy inputs

Total food processing energy use.

```{r, message = FALSE, warning = FALSE}
food_pro_energy_inputs_edit <- food_pro_inputs %>%
  filter(!grepl("water", input)) %>%
  mutate(input_edit = case_when(input == "elect_td_ind" ~ "electricity",
                                input == "refined liquids industrial" ~ "refined liquids",
                                input == "delivered biomass" ~ "biomass",
                                input == "delivered coal" ~ "coal",
                                input == "wholesale gas" ~ "gas",
                                input == "global solar resource" ~ "solar",
                                TRUE ~ input))

ggplot(food_pro_energy_inputs_edit %>% filter(scenario == ref_scenario_name & branch == food_branch_name & year >= 2005),
       aes(x = year, y = value, fill = input_edit)) +
  geom_col() +
  facet_wrap(~region, ncol = 8, scale = "free_y") +
  scale_fill_manual(values = pal_sel_extended, drop = TRUE, limits = force, name = "fuel") +
  labs(x = "", y = "EJ", title = "Energy inputs to food processing and process heat food processing, reference scenario, food industry branch") +
  theme_bw() +
  theme(text=element_text(size=22),
        strip.background = element_blank())
ggsave(paste0(fig_dir, "/food_pro_total_energy_inputs_ref_food_ind.png"), width = 30, height = 20)

ggplot(food_pro_energy_inputs_edit %>% filter(scenario == ref_scenario_name & branch == food_branch_name & year >= 2005),
       aes(x = year, y = value, fill = input_edit)) +
  geom_col() +
  scale_fill_manual(values = pal_sel_extended, drop = TRUE, limits = force, name = "fuel") +
  labs(x = "", y = "EJ", title = "Global energy inputs to food processing and process heat food processing\nReference scenario, food industry branch") +
  theme_bw() +
  theme(text=element_text(size=17),
        strip.background = element_blank())
ggsave(paste0(fig_dir, "/food_pro_total_energy_inputs_ref_food_ind_global.png"), width = 10, height = 8)
```

Food processing overall sector inputs.

```{r, message = FALSE, warning = FALSE}
food_pro_energy_inputs_overall_sector <- inputs_tech %>%
  filter(sector == "food processing" & !grepl("water", input)) %>%
  mutate(input = if_else(input == "elect_td_ind", "electricity", input))

ggplot(food_pro_energy_inputs_overall_sector %>% filter(scenario == ref_scenario_name & branch == food_branch_name & year >= 2005),
       aes(x = year, y = value, fill = input)) +
  geom_col() +
  facet_wrap(~region, ncol = 8, scale = "free_y") +
  scale_fill_manual(values = pal_sel_extended, drop = TRUE, limits = force, name = "fuel") +
  labs(x = "", y = "EJ", title = "Energy inputs to food processing, reference scenario, food industry branch") +
  theme_bw() +
  theme(text=element_text(size=22),
        strip.background = element_blank())
ggsave(paste0(fig_dir, "/food_pro_overall_sector_energy_inputs_ref_food_ind.png"), width = 30, height = 20)

ggplot(food_pro_energy_inputs_overall_sector %>% filter(scenario == ref_scenario_name & branch == food_branch_name & year >= 2005),
       aes(x = year, y = value, fill = input)) +
  geom_col() +
  scale_fill_manual(values = pal_sel_extended, drop = TRUE, limits = force, name = "fuel") +
  labs(x = "", y = "EJ", title = "Global energy inputs to food processing\nReference scenario, food industry branch") +
  theme_bw() +
  theme(text=element_text(size=17),
        strip.background = element_blank())
ggsave(paste0(fig_dir, "/food_pro_overall_sector_energy_inputs_ref_food_ind_global.png"), width = 10, height = 8)
```

Process heat food processing energy inputs.

```{r, message = FALSE, warning = FALSE}
food_pro_process_heat_energy_inputs_edit <- food_pro_inputs_process_heat_sep %>%
  filter(!grepl("water", input) & sector == "process heat food processing") %>%
  mutate(input_edit = case_when(input == "elect_td_ind" ~ "electricity",
                                input == "refined liquids industrial" ~ "refined liquids",
                                input == "delivered biomass" ~ "biomass",
                                input == "delivered coal" ~ "coal",
                                input == "wholesale gas" ~ "gas",
                                input == "global solar resource" ~ "solar",
                                TRUE ~ input))

ggplot(food_pro_process_heat_energy_inputs_edit %>% 
         filter(scenario == ref_scenario_name & branch == food_branch_name & year >= 2005),
       aes(x = year, y = value, fill = input_edit)) +
  geom_col() +
  facet_wrap(~region, ncol = 8, scale = "free_y") +
  scale_fill_manual(values = pal_sel_extended, drop = TRUE, limits = force, name = "technology") +
  labs(x = "", y = "EJ", title = "Energy inputs to process heat food processing, reference scenario, food industry branch") +
  theme_bw() +
  theme(text=element_text(size=22),
        strip.background = element_blank())
ggsave(paste0(fig_dir, "/food_pro_process_heat_energy_inputs_ref_food_ind.png"), width = 30, height = 20)

ggplot(food_pro_process_heat_energy_inputs_edit %>% 
         filter(scenario == ref_scenario_name & branch == food_branch_name & year >= 2005),
       aes(x = year, y = value, fill = input_edit)) +
  geom_col() +
  scale_fill_manual(values = pal_sel_extended, drop = TRUE, limits = force, name = "technology") +
  labs(x = "", y = "EJ", title = "Global energy inputs to process heat food processing\nReference scenario, food industry branch") +
  theme_bw() +
  theme(text=element_text(size=17),
        strip.background = element_blank())
ggsave(paste0(fig_dir, "/food_pro_process_heat_energy_inputs_ref_food_ind_global.png"), width = 10, height = 8)
```

Food processing energy use coefficient per calorie consumed.

```{r, message = FALSE, warning = FALSE}
# get total energy use
food_pro_energy_total <- food_pro_energy_inputs_edit %>%
  group_by(scenario, branch, region, year) %>%
  summarize(EJ = sum(value)) %>%
  ungroup()

# get electricity + process heat inputs
food_pro_energy_elec_process_total <- food_pro_energy_inputs_overall_sector %>%
  group_by(scenario, branch, region, year) %>%
  summarize(EJ_elec_process = sum(value)) %>%
  ungroup()

# get coefficient of energy use per calorie consumed 
food_pro_coef <- food_pro_energy_total %>%
  left_join(food_pro_energy_elec_process_total) %>%
  left_join(food_demand_total %>%
              dplyr::select(scenario, branch, region, year, Pcal = value)) %>%
  mutate(coef_primary_energy = EJ / Pcal,
         coef_electricity_process_heat = EJ_elec_process / Pcal) %>%
  dplyr::select(-c(EJ, EJ_elec_process, Pcal)) %>%
  pivot_longer(c(coef_primary_energy, coef_electricity_process_heat), names_to = "coef_type", values_to = "value")

ggplot(food_pro_coef %>% filter(scenario == ref_scenario_name & branch == food_branch_name & year >= 2005),
       aes(x = year, y = value, color = coef_type)) +
  geom_line(size = 1) + 
  facet_wrap(~region, ncol = 8) +
  labs(x = "", y = "EJ per Pcal", title = "Food processing energy use coefficient, reference scenario, food industry branch") + 
  theme_bw() + 
  theme(text=element_text(size=22),
        strip.background = element_blank())
ggsave(paste0(fig_dir, "/food_pro_energy_use_coef_ref_food_ind.png"), width = 30, height = 20)
```

### Food processing sector carbon emissions

```{r, message = FALSE, warning = FALSE}
# convert all emissions to CO2 from C
CO2_emis_sector <- CO2_emis_sector %>%
  mutate(Mt_CO2 = value * C_to_CO2)
CO2_emis_sector_no_bio <- CO2_emis_sector_no_bio %>% 
  mutate(Mt_CO2 = value * C_to_CO2)
CO2_emis_region <- CO2_emis_region %>%
  mutate(Mt_CO2 = value * C_to_CO2)
LUC_emis_region <- LUC_emis_region  %>%
  mutate(Mt_CO2 = value * C_to_CO2)

# get global
CO2_emis_sector_global <- CO2_emis_sector %>%
  group_by(scenario, branch, sector, year) %>%
  summarize(Mt_CO2 = sum(Mt_CO2)) %>%
  ungroup()
CO2_emis_sector_no_bio_global <- CO2_emis_sector_no_bio %>%
  group_by(scenario, branch, sector, year) %>%
  summarize(Mt_CO2 = sum(Mt_CO2)) %>%
  ungroup()
CO2_emis_global <- CO2_emis_region %>%
  group_by(scenario, branch, year) %>%
  summarize(Mt_CO2 = sum(Mt_CO2)) %>%
  ungroup()
LUC_emis_global <- LUC_emis_region %>%
  group_by(scenario, branch, year) %>%
  summarize(Mt_CO2 = sum(Mt_CO2)) %>%
  ungroup()

# get total CO2 emissions
CO2_emis_global_w_LUC <- CO2_emis_global %>%
  mutate(emis_type = "FFI") %>%
  rbind(LUC_emis_global %>% 
          mutate(emis_type = "LUC") %>%
          filter(year %in% unique(CO2_emis_global$year)))

CO2_emis_global_w_LUC_total <- CO2_emis_global_w_LUC %>%
  group_by(scenario, branch, year) %>% 
  summarize(Mt_CO2 = sum(Mt_CO2)) %>%
  ungroup()

# note that because the food processing overall sector takes in only process heat food processing and electricity, it has no associated direct emissions
# all food processing emissions come from the process heat food processing sector
ggplot(CO2_emis_sector_no_bio %>% 
         filter(scenario == ref_scenario_name & branch == food_branch_name & year >= 2005 & sector == "process heat food processing"),
       aes(x = year, y = Mt_CO2)) +
  geom_line(size = 1) + 
  facet_wrap(~region, nrow = 4) + 
  labs(x = "", y = "Mt CO2", title = "Food processing CO2 emissions (no bio), reference scenario, food industry branch") + 
  theme_bw() + 
  theme(text=element_text(size=22),
        strip.background = element_blank())
ggsave(paste0(fig_dir, "/CO2_emissions_no_bio_food_pro_region_ref_food_ind.png"), width = 30, height = 20)

ggplot(CO2_emis_sector_no_bio_global %>% 
         filter(scenario == ref_scenario_name & branch == food_branch_name & year >= 2005 & sector == "process heat food processing"),
       aes(x = year, y = Mt_CO2)) +
  geom_line(size = 1) + 
  labs(x = "", y = "Mt CO2", title = "Global food processing CO2 emissions (no bio)\nReference scenario, food industry branch") + 
  theme_bw() + 
  theme(text=element_text(size=17),
        strip.background = element_blank())
ggsave(paste0(fig_dir, "/CO2_emissions_no_bio_food_pro_region_ref_food_ind_global.png"), width = 10, height = 8)
```

### Industry energy use by sector

```{r, message = FALSE, warning = FALSE}
# aggregate industry sectors
industry_final_en_sector_agg <- industry_final_en_tech_fuel %>%
  filter(sector %in% industry_sectors) %>%
  left_join(industry_sector_agg) %>%
  group_by(Units, scenario, branch, region, sector_agg, year) %>%
  summarize(value = sum(value)) %>%
  ungroup()

# aggregate to total industry
industry_final_en_sector_agg_total <- industry_final_en_sector_agg %>%
  group_by(scenario, branch, region, year, Units) %>%
  summarize(value = sum(value)) %>%
  ungroup()

industry_final_en_sector_agg_total_global <- industry_final_en_sector_agg_total %>%
  group_by(scenario, branch, year, Units) %>%
  summarize(value = sum(value)) %>%
  ungroup()

ggplot(industry_final_en_sector_agg %>% filter(scenario == ref_scenario_name & branch == food_branch_name & year >= 2005),
       aes(x = year, y = value, fill = sector_agg)) +
  geom_col() +
  facet_wrap(~region, nrow = 4) +
  scale_fill_manual(values = pal_industry_sectors, name = "sector") +
  labs(x = "", y = "EJ", title = "Industry final energy use by sector, reference scenario, food industry branch") +
  theme_bw() +
  theme(text=element_text(size=22),
        strip.background = element_blank())
ggsave(paste0(fig_dir, "/industry_final_en_sector_ref_food_ind.png"), width = 30, height = 20)

ggplot(industry_final_en_sector_agg %>% filter(scenario == ref_scenario_name & branch == food_branch_name & year >= 2005),
       aes(x = year, y = value, fill = sector_agg)) +
  geom_col() +
  scale_fill_manual(values = pal_industry_sectors, name = "sector") +
  labs(x = "", y = "EJ", title = "Global industry final energy use by sector\nReference scenario, food industry branch") +
  theme_bw() +
  theme(text=element_text(size=17),
        strip.background = element_blank())
ggsave(paste0(fig_dir, "/industry_final_en_sector_global_ref_food_ind.png"), width = 10, height = 8)
```


### Industry carbon emissions by sector

```{r, message = FALSE, warning = FALSE}
# aggregate sectors
CO2_emis_sector_no_bio_industry_agg <- CO2_emis_sector_no_bio %>%
  filter(sector %in% industry_sectors) %>%
  left_join(industry_sector_agg) %>%
  group_by(scenario, branch, region, sector_agg, year) %>%
  summarize(value = sum(value), Mt_CO2 = sum(Mt_CO2)) %>%
  ungroup()

CO2_emis_sector_no_bio_industry_agg_global <- CO2_emis_sector_no_bio_industry_agg  %>%
  group_by(scenario, branch, sector_agg, year) %>%
  summarize(value = sum(value),
            Mt_CO2 = sum(Mt_CO2)) %>%
  ungroup()

# aggregate to total industry
CO2_emis_sector_no_bio_industry_agg_total <- CO2_emis_sector_no_bio_industry_agg %>%
  group_by(scenario, branch, region, year) %>%
  summarize(Mt_CO2 = sum(Mt_CO2)) %>%
  ungroup()

CO2_emis_sector_no_bio_industry_agg_total_global <- CO2_emis_sector_no_bio_industry_agg_total %>%
  group_by(scenario, branch, year) %>%
  summarize(Mt_CO2 = sum(Mt_CO2)) %>%
  ungroup()
  
ggplot(CO2_emis_sector_no_bio_industry_agg %>% filter(scenario == ref_scenario_name & branch == food_branch_name & year >= 2005),
       aes(x = year, y = Mt_CO2, fill = sector_agg)) +
  geom_col() + 
  scale_fill_manual(values = pal_industry_sectors, name = "sector") + 
  facet_wrap(~region, nrow = 4, scales = "free_y") + 
  labs(x = "", y = "Mt CO2", title = "Industry CO2 emissions (no bio), reference scenario, food industry branch") + 
  theme_bw() + 
  theme(text=element_text(size=22),
        strip.background = element_blank())
ggsave(paste0(fig_dir, "/CO2_emissions_no_bio_industry_sector_agg_region_ref_food_ind.png"), width = 30, height = 20)

ggplot(CO2_emis_sector_no_bio_industry_agg_global %>% filter(scenario == ref_scenario_name & branch == food_branch_name & year >= 2005),
       aes(x = year, y = Mt_CO2, fill = sector_agg)) +
  geom_col() + 
  scale_fill_manual(values = pal_industry_sectors, name = "sector") + 
  labs(x = "", y = "Mt CO2", title = "Global industry CO2 emissions (no bio)\nReference scenario, food industry branch") + 
  theme_bw() + 
  theme(text=element_text(size=17),
        strip.background = element_blank())
ggsave(paste0(fig_dir, "/CO2_emissions_no_bio_industry_sector_agg_region_ref_food_ind_global.png"), width = 10, height = 8)
```


### Industry non-CO2 emissions by sector

```{r, message = FALSE, warning = FALSE}
# get industry non-CO2 emissions
nonCO2_emis_sector_CO2eq_industry <- nonCO2_emis_sector %>%
  filter(sector %in% industry_sectors) %>%
  left_join(GWP_AR5 %>% rename(GHG = ghg)) %>%
  filter(!is.na(GWP)) %>%
  mutate(Mt_CO2e = value * GWP)

nonCO2_emis_sector_total_CO2eq_industry <- nonCO2_emis_sector_CO2eq_industry %>%
  group_by(scenario, branch, region, sector, year) %>%
  summarize(Mt_CO2e = sum(Mt_CO2e)) %>%
  ungroup()

# aggregate sectors
nonCO2_emis_sector_total_CO2eq_industry_agg <- nonCO2_emis_sector_total_CO2eq_industry %>%
  left_join(industry_sector_agg) %>%
  group_by(scenario, branch, region, sector_agg, year) %>%
  summarize(Mt_CO2e = sum(Mt_CO2e)) %>%
  ungroup()

# aggregate to total industry
nonCO2_emis_sector_total_CO2eq_industry_agg_total <- nonCO2_emis_sector_total_CO2eq_industry_agg %>%
  group_by(scenario, branch, region, year) %>%
  summarize(Mt_CO2e = sum(Mt_CO2e)) %>%
  ungroup()

nonCO2_emis_sector_total_CO2eq_industry_agg_total_global <- nonCO2_emis_sector_total_CO2eq_industry_agg_total %>%
  group_by(scenario, branch, year) %>%
  summarize(Mt_CO2e = sum(Mt_CO2e)) %>%
  ungroup()

ggplot(nonCO2_emis_sector_total_CO2eq_industry_agg %>% filter(scenario == ref_scenario_name & branch == food_branch_name & year >= 2005),
       aes(x = year, y = Mt_CO2e, fill = sector_agg)) +
  geom_col() + 
  scale_fill_manual(values = pal_industry_sectors, name = "sector") + 
  facet_wrap(~region, nrow = 4, scales = "free_y") + 
  labs(x = "", y = "Mt CO2e", title = "Industry GHG emissions, reference scenario, food industry branch") + 
  theme_bw() + 
  theme(text=element_text(size=22),
        strip.background = element_blank())
ggsave(paste0(fig_dir, "/GHG_emissions_industry_sector_region_ref_food_ind.png"), width = 30, height = 20)

ggplot(nonCO2_emis_sector_total_CO2eq_industry_agg %>% filter(scenario == ref_scenario_name & branch == food_branch_name & year >= 2005),
       aes(x = year, y = Mt_CO2e, fill = sector_agg)) +
  geom_col() + 
  scale_fill_manual(values = pal_industry_sectors, name = "sector") + 
  labs(x = "", y = "Mt CO2e", title = "Global industry GHG emissions\nReference scenario, food industry branch") + 
  theme_bw() + 
  theme(text=element_text(size=17),
        strip.background = element_blank())
ggsave(paste0(fig_dir, "/GHG_emissions_industry_sector_region_ref_food_ind_global.png"), width = 10, height = 8)
```

### Industry water withdrawals by sector

```{r, message = FALSE, warning = FALSE}
# water withdrawals
industry_water_withdrawals <- industry_water_withdrawals_consumption %>% 
  filter(input == "water_td_ind_W")

industry_water_withdrawals_global <- industry_water_withdrawals %>%
  filter(region != "Global") %>%
  group_by(Units, scenario, branch, sector, input, year) %>%
  summarize(value = sum(value)) %>%
  ungroup()

ggplot(industry_water_withdrawals %>% filter(scenario == ref_scenario_name & branch == food_branch_name & year >= 2005 & !grepl("H2", sector)),
       aes(x = year, y = value, fill = sector)) +
  geom_col() +
  facet_wrap(~region, ncol = 4, scales = "free_y") + 
  scale_fill_manual(values = c("other industry" = "darkred", "paper" = "darkblue", "food processing" = "green")) + 
  labs(x = "", y = "km^3", title = "Industry water withdrawals, reference scenario, food industry branch") + 
  theme_bw() + 
  theme(text=element_text(size=22),
        strip.background = element_blank())
ggsave(paste0(fig_dir, "/industry_water_withdrawals_ref_food_ind.png"), width = 30, height = 20)

ggplot(industry_water_withdrawals_global %>% filter(scenario == ref_scenario_name & branch == food_branch_name & year >= 2005 & !grepl("H2", sector)),
       aes(x = year, y = value, fill = sector)) +
  geom_col() +
  scale_fill_manual(values = c("other industry" = "darkred", "paper" = "darkblue", "food processing" = "green")) + 
  labs(x = "", y = "km^3", title = "Global industry water withdrawals\nReference scenario, food industry branch") + 
  theme_bw() + 
  theme(text=element_text(size=17),
        strip.background = element_blank())
ggsave(paste0(fig_dir, "/industry_water_withdrawals_ref_food_ind_global.png"), width = 10, height = 8)
```


## SSP/RCP results

### Food processing total energy use

### Food processing energy use by fuel

### Process heat food processing outputs by technology

### Food processing carbon emissions

### Food processing prices

### Total carbon emissions


# Comparison to master branch

## Reference scenario

### Industry energy use

Total industry energy use.

```{r, message = FALSE, warning = FALSE}
# compare total industry energy use across regions and globally
ggplot(industry_final_en_sector_agg_total %>% filter(((scenario == ref_scenario_name & branch == food_branch_name) | (scenario == ref_scenario_name_master & branch == master_branch_name)) & year >= 2005),
       aes(x = year, y = value, linetype = branch)) +
  geom_line(size = 1) + 
  scale_linetype_manual(values = c("dashed", "solid")) + 
  scale_fill_manual(values = pal_industry_sectors, name = "sector") + 
  facet_wrap(~region, nrow = 4, scales = "free_y") + 
  labs(x = "", y = "EJ", title = "Total industry energy use, reference scenario") + 
  theme_bw() + 
  theme(text=element_text(size=22),
        strip.background = element_blank())
ggsave(paste0(fig_dir, "/total_industry_energy_use_ref_comp.png"), width = 30, height = 20)

ggplot(industry_final_en_sector_agg_total_global %>% filter(((scenario == ref_scenario_name & branch == food_branch_name) | (scenario == ref_scenario_name_master & branch == master_branch_name)) & year >= 2005),
       aes(x = year, y = value, linetype = branch)) +
  geom_line(size = 1) + 
  scale_linetype_manual(values = c("dashed", "solid")) + 
  scale_fill_manual(values = pal_industry_sectors, name = "sector") + 
  labs(x = "", y = "EJ", title = "Global total industry energy use, reference scenario") + 
  theme_bw() + 
  theme(text=element_text(size=17),
        strip.background = element_blank())
ggsave(paste0(fig_dir, "/total_industry_energy_use_ref_comp_global.png"), width = 10, height = 8)
```

Industry energy use by sector.

Industry energy use by fuel.

### Industry carbon emissions

Total and by sector

### Industry non-CO2 emissions

Total and by sector

### Industry water withdrawals

Total and by sector

### Total carbon emissions


## SSP/RCP results

